Calculate FD

### 2020-07-29 analysis/calc_fd.Rmd
Write out attempted files

  print(filter_plot)

@@

remain <- data %>%
  filter(!plot_id %in% fd_data$plot_id, !plot_id %in% c(1661, 196456, 3721, 3601))

>>>>

  fs::dir_create(paste0(here::here("data"), "/fd_attempt"))
  write_tsv(data.frame(), paste0(here::here("data"), "/fd_attempt/", filter_plot, ".tsv"))

@@

attempted <- dir(here::here("data", "fd_attempt"), "*.tsv") %>%
  str_replace(".tsv", "") %>%
  as.numeric()

remain <- data %>%
  filter(!plot_id %in% fd_data$plot_id, 
         !plot_id %in% attempted,
         !plot_id %in% c(1661, 196456, 3721, 3601, 2171))#1952507
